Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-02-05 article/06_Remarks.Rmd
more work on the conclusion
used the right sentence for funding declaration

I would like to offer my special thanks to my supervisors PD Dr. Oliver Nakoinz (University of Kiel) and Dr. Martin Hinz (University of Bern) for developing this research idea with me and for ongoing support and advice before, while and after the creation of the master thesis this article is based on. I had helpful discussions at different stages of the research process with Dr. Jutta Kneisel, Dr. Christoph Rinne, Dr. Daniel Knitter, Dr. Nils Müller-Scheeßel and David Matzig, B.A. (all University of Kiel). Beyond these colleagues at Kiel University I am particularly grateful for the feedback, encouragement and literature recommendations by Prof. Dr. Ben Marwick (University of Washington) and the valuable C++ code review by Benny Baumann.

@@

This paper was prepared without financial support, except for a 300Euro travel grant to attend the Conference on Complex Systems 2018 by the International Center of Kiel University.

>>>>

I would like to offer my special thanks to my supervisors PD Dr. Oliver Nakoinz (University of Kiel) and Dr. Martin Hinz (University of Bern) for developing this research idea with me and for ongoing support and advice before, while and after the creation of the master thesis this article is based on. I had helpful discussions at different stages of the research process with Dr. Jutta Kneisel, Dr. Christoph Rinne, Dr. Daniel Knitter, Dr. Nils Müller-Scheeßel and David Matzig, B.A. (all University of Kiel). Beyond these colleagues at Kiel University I am particularly grateful for the feedback, encouragement and literature recommendations by Prof. Dr. Ben Marwick (University of Washington) and the valuable C++ code review by Benny Baumann (Kiel).

@@

This research received no specific grant from any funding agency in the public, commercial, or not-for-profit sectors, except for a 300Euro travel grant to attend the Conference on Complex Systems 2018 by the International Center of Kiel University.
